Reaction Barrier Analysis

### 2024-12-02 Code/ReactionBarrierAnalysis.Rmd
final edits made just before submission

---
title: "Reaction Barrier Analysis"
author: "Owen Fiore"
date: "2024-11-28"
output: html_document
---

@@

We considered many families of models, and formula structures within the
generalized Gamma but thought that the results from the `gg3b` game strong
results.  The first term corresponds to the $\mu$ term of the model, which is
a random effect for `Venue`. $\sigma$ contains a random effect for `Heat`.
```{r}
gg3b <- gamlss(RxnTime ~ random(Venue), sigma.formula = ~ random(Heat),
               data = dhm, family = GG, control = gamlss.control(n.cyc = 40))

@@

We are going to see what happens when we pool men's and women's data together.
We sill need to separate by year but will have 3 analyses instead of 6.  As a
result of the larger data set we are going to run the permutation tests at a
size of $n = 100,000$ rather than $n = 1,000,000$ as the code takes several
hours to run otherwise.  The asymptotic results are all highly statistically
significant, and with the larger data sets, the results from the asymptotic
tests should be of higher quality.

@@

Need to talk about results after running code

@@

### Women's Gamlss
We decided to separate women's results after numerous papers suggested that
men and women have differing reaction times, but we still thought it was important
to investigate what an appropriate reaction time barrier was for women.  The
women's data is very similar to the men's, but there is not data from 1999
available for women and the women compete in the 100 meter hurdle instead of the
110 meter hurdle.  We are going to replicate many of the same methods used above
for the men's results.

@@

Let us see how we did with residuals
```{r}
qq_conf_plot(resid(gg3b_nodq))
```
The standardized residual plot looks quite strong.  We are now ready to simulate
to examine how extreme certain reaction times are.

>>>>

---
title: "Reaction Barrier Analysis"
author: "Blinded"
date: "2024-11-28"
output: html_document
---

@@

We considered many families of models, and formula structures within the
generalized Gamma, but found that `gg3b` gave strong results based on AIC.  
The first term corresponds to the $\mu$ term of the model, which is
a random effect for `Venue`. $\sigma$ contains a random effect for `Heat`.
```{r}
gg3b <- gamlss(RxnTime ~ random(Venue), sigma.formula = ~ random(Heat),
               data = dhm, family = GG, control = gamlss.control(n.cyc = 40))

@@

We are going to see what happens when we pool men's and women's data together.
We still need to separate by year but will have 3 analyses instead of 6.  As a
result of the larger data set we are going to run the permutation tests at a
size of $B = 100,000$ rather than $B = 1,000,000$ as the code takes several
hours to run otherwise.  The asymptotic results are all highly statistically
significant, and with the larger data sets, the results from the asymptotic
tests should be of higher quality.

@@

@@

### Women's GAMLSS
We decided to separate women's results after numerous papers suggested that
men and women have differing reaction times, but we still thought it was important
to investigate what an appropriate reaction time barrier was for women.  The
women's data is very similar to the men's, but there is not data from 1999
available for women and the women compete in the 100 meter hurdle instead of the
110 meter hurdle.  We are going to replicate many of the same methods used above
for the men's results.

@@

Let us see how we did with residuals
```{r}
qq_conf_plot(resid(gg3b_nodq))
```
The standardized residual plot looks quite good.  We are now ready to simulate
to examine how extreme certain reaction times are.
